\documentclass[11pt]{article}

\usepackage{color}
\usepackage{eacl2014}
\usepackage{latexsym}
\usepackage{listings}
\usepackage{natbib}
\usepackage{times}
\usepackage{url}

\special{papersize=210mm,297mm}

\bibliographystyle{apalike}

\definecolor{Brown}{cmyk}{0,0.81,1,0.60}
\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{CadetBlue}{cmyk}{0.62,0.57,0.23,0}
\definecolor{lightlightgray}{gray}{0.9}

\lstset{
    language=haskell,                       % Code langugage
    basicstyle=\footnotesize\ttfamily,      % Code font, Examples: \footnotesize, \ttfamily
    keywordstyle=\color{OliveGreen},        % Keywords font ('*' = uppercase)
    commentstyle=\color{gray},              % Comments font
    backgroundcolor=\color{lightlightgray}, % Choose background color
    tabsize=2,                              % Default tab size
    captionpos=b,                           % Caption-position = bottom
    breaklines=true,                        % Automatic line breaking?
    breakatwhitespace=false,                % Automatic breaks only at whitespace?
    showspaces=false,                       % Dont make spaces visible
    showtabs=false,                         % Dont make tabls visible
    frame=single,
    framesep=3pt,
    mathescape=true,
    xleftmargin=3pt,
    xrightmargin=3pt
}

\title{Artificial Intelligence Project}
\author{Andreas Arvidsson \\
  {\tt andarv@student.chalmers.se} \\
  Sebastian Lagerman \\
  {\tt seblag@student.chalmers.se} \\
  Johan Swetz\'{e}n \\
  {\tt swetzen@student.chalmers.se} \\
  Robin Touche \\
  {\tt robint@student.chalmers.se} \\}

\date{}

\begin{document}
\maketitle

% 5. Miscellaneous uretionalistics(?)

% 6. Literal use survey

% INCLUDE SOME EXAMPLES OF BOTH GOOD AND BAD SITUATIONS

% not naturel language, but controlled naturel language.
% No programming language terms
% - Software development terms can be used
%   Examples: (FIGURE/FLOWCHART)
% -> utterance -> parse tree -> PDDL goals -A-> PDDL goal -P-> actions
% Pseudo code snippets
% use template provided
% individual contibutions
% 8 pages + appendix/references

\input{./introduction.tex}

\input{./parser.tex}

\input{./interpreter.tex}

\input{./ambiguity.tex}

\input{./planner.tex}

\section*{Extensions}
\begin{itemize}
\iten Ambiguity resolution by listing possible different objects, eg. ``You could mean the Yellow Box or the Red Box'', if the user wanted to pick ``the large box'' although there were two of them.
\item Find the shortest solution, measured by the number of pick and drops. This is inherent to the A* algorithm that we are using.
\item Support for differentiating between quantifiers. `a' and `any' means the same, but `the' requires the specification to refer to a single object, or we output an ambiguity error.
\end{itemize}

\section*{Final thoughts}
The project was immensely helpful for our understanding of artificial intelligence for problem solving. It would've been nice if all the groups didn't have exactly the same problem, since we had some cool ideas and watching the same solution in the presentation slots might be a bit boring.

Our project organization could perhaps have been a little better planned with regards to the structure of the code.
Late in the project, when we needed to handle errors in a nice way from the user's perspective, we realized that using monads for this would be a nice solution.
If we'd begun with this realization (which could have been achieved with more discussions and meetings), we'd have saved some time.

Finally, we did not use a Scrum tool like PivotalTracker. If we would have done this, the project might have finished quicker - but unfortunately we realized this a bit too late.
Instead, we mainly used github's issue tracking system for long-lasting bugs (which there weren't many of).

\newpage
\input{./contributions.tex}

\newpage
\bibliography{references}

\end{document}
